Title Reproducible Research: Peer Assessment 1
========================================================



## Loading and preprocessing the data
```{r}
activity = read.csv("activity.csv")
library(plyr)
goodactivity = subset(activity, !is.na(steps))
dailyactivity = ddply(goodactivity,.(date),summarize, steps = sum(steps))
```


## What is mean total number of steps taken per day?
```{r histogram, fig.ehight=4}
hist(dailyactivity$steps, main="Daily Steps", xlab="Days",breaks=10)
meansteps = mean(dailyactivity$steps)
mediansteps = median(dailyactivity$steps)
```
### Overall Mean Value - `r meansteps`
### Overall Median Value - `r mediansteps`

## What is the average daily activity pattern?
```{r averagedailyactivity, fig.height=4}
averagesteps = ddply(goodactivity, .(interval), summarize, avgsteps = mean(steps))
plot(averagesteps$interval, averagesteps$avgsteps,type="l", main = "Average Steps By Interval", xlab="5mins Interval", ylab ='Average Steps')
```

## Imputing missing values
```{r}
maxintervaldf = subset(averagesteps, avgsteps == max(averagesteps$avgsteps))
maxinterval = maxintervaldf$interval
```
### Interval with max average steps - `r maxinterval`

## Imputing missing values
```{r}
missingdata = subset(activity, is.na(steps))
missingdatavalues = merge(missingdata, averagesteps[,c("avgsteps","interval")])
missingdatavalues = data.frame(missingdatavalues$avgsteps,missingdatavalues$date,missingdatavalues$interval)
colnames(missingdatavalues) = c("steps","date","interval")
fullactivity<-rbind(goodactivity,missingdatavalues)
dailyfullactivity = ddply(fullactivity,.(date),summarize, steps = sum(steps))
```

## What is mean total number of steps taken per day with missing value filled in?
```{r histogram2, fig.ehight=4}
hist(dailyfullactivity$steps, main="Daily Steps", xlab="Days",breaks=10)
meansteps = mean(dailyfullactivity$steps)
mediansteps = median(dailyfullactivity$steps)
```
### Overall Mean Value with missing valuyes filled in  - `r meansteps`
### Overall Median Value with missing values filled in - `r mediansteps`


## Are there differences in activity patterns between weekdays and weekends?
```{r}
summary(cars)
```
```{r fig.width=7, fig.height=6}
plot(cars)
```

